---
title: "R Project 1 - Hello R"
author: "Chiagozie Uwalaka"
date: "Due Fed 3rd"
output: 
  html_document: 
    fig_height: 8
    highlight: textmate
    theme: cerulean
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
 The datasaurus_dozen file has 1846 rows and 3 columns/variables.The Variables includes: data set, x, and y.

### Exercise 2
dino_data <- datasaurus_dozen %>%
filter(dataset == "dino")
dino_data %>%
summarize(r = cor(x,y))

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3
The correlation Coefficient for the star graph is -0.630 all though it is similar to the dino data due to them both being non-linear, they have a difference -.015.
```{r}

```

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```

I'm some text, you should replace me with more meaningful text...
 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

The correlation coeffiecient for the circle has a -.0038 differece from the dino with the circle being -.0683 and the dino being -.0645. 

```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)

```{r plot-all shapes}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

```{r cor-all shapes}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(26)
```

